\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Obstacles}
Depending on the flight path of the ball and where the ball lands, there may be obstacles in the way. 

\subsection{Water}
When a ball lands in water, the ball is lost. The player will count that round as a stroke, and place the ball on the closest land hex of their choice. 

\subsection{Bunkers}
A bunker reduces the power of the player's next hit. While in a bunker, reduce the power of the swing by 2. For example, you have four dice showing a value of 2 - 5, your original power is a 4. Because you are in the bunker, your power is now a 2. If a your original power is a 2 or less, it is considered a failed shot and the ball doesn't move. It counts as a stroke, and the player repeats the round. 

\subsection{Trees}
When the flight path of the ball is blocked by a tree, an additional roll is required to see if the ball stops or continues through the tree. Pick up a D6 and roll it.
\begin{enumerate}
    \item If the value is 2 - 5, the ball continues through the tree, as if it was not there. 
    \item If the value is a 1 or 6, the ball hits the tree and lands or stops at the previous hex. 
\end{enumerate}
If the ball is going through a series of trees, repeat the above steps for every tree. If the ball is stopped at any point, the player places the ball on the closest open hex of their choice. 

\subsection{Cart Path}
When the ball lands on a cart path hex, it will bounce 1 hex more in the direction it was traveling when entering the cart path hex. 

\subsection{Out of Bounds}
When the ball lands out of bounds, the player will add a stroke to their score and place the ball on the last land hex the ball had previously traveled over. 
\end{document}